A Review of Lossless Data Compression Methods

### 2018-11-19 paper.tex
Add DEFLATE.

One such improvement was the Lempel-Ziv-Welch compression algorithm,
commonly referred to as LZW. It was created as an extension of the
Lempel-Ziv algorithm which was introduced soon after the publication
of the original LZ77. The LZW variant is extremely widespread in
applications; for instance, one of its many uses is as part of the GIF
image format. LZW's improvements upon the LZ algorithm are fairly
straightforward, but they allow for significant improvements to the
simplicity of implementation. According to the author, the LZW
algorithm can take operate at a speed of three clock cycles (CPU
instructions) per input symbol. \cite{LempelZivWelch}

@@

The LZ family of compression codes is massive, and LZW is just one
single member. Another, possibly even more widespread variant is the
DEFLATE algorithm.

@@

>>>>

One such improvement was the Lempel-Ziv-Welch compression algorithm,
commonly referred to as LZW. It was created as an extension of the
Lempel-Ziv algorithm and was introduced soon after the publication of
the original LZ77. The LZW variant is extremely widespread in
applications; for instance, one of its many uses is as part of the GIF
image format. LZW's improvements upon the LZ algorithm are fairly
straightforward, but they allow for significant improvements to the
simplicity of implementation. According to the author, the LZW
algorithm can take operate at a speed of three clock cycles (CPU
instructions) per input symbol. \cite{LempelZivWelch}

@@

The LZ family of compression codes is massive, and LZW is just one
single member. Possibly even more widespread is the DEFLATE algorithm,
used in many compressed file formats.

@@

In general, compression proceeds as follows: for a given block of data
withint the input, the algorithm constructs a Huffman prefix coding
for the input alphabet. Information about the prefix coding is then
stored within the output block header, which contains metadata about the
compressed output. DEFLATE supports ``fixed'' and ``dynamic'' Huffman
codes. Fixed Huffman codes are defined in the DEFLATE specification
and can be simply hard-coded in the compressor/decompressor
software. Dynamic Huffman codes, on the other hand, are created by the
compressor and their information is serialized and stored in the block
header. The compressed data is then run through an implementation of
the LZ77 algorithm from earlier.

DEFLATE allows us to reap the benefits both of the the LZ77 algorithm
as well as the more basic Huffman prefix coding scheme, all while
using a more-or-less standardized file format for easy interchange.
